%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\vspace{5pt}
%---------------------------------------------------------


\cventry 
%---------------------------------------------------------
    {\textbf{Lecturer} } % Job title
    {Azad University - Isfahan (Najafabad) Branch} % Organization
    {Isfahan, Iran} % Location
    {June. 2019 - Aug. 2021} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {CE-EN0104 - Structural Analysis I	\hfill			Sept. 2019 – Dec. 2020 }
		\item {CE-EN0114 - Steel Structures	\hfill			Jan. 2020 - May 2021}
	\end{cvitems}   
     }

      \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Intern \& Structural Supervision }} % Job title
    {Abadgaran-Amin road and Building Company} % Organization
    {Isfahan, Iran} % Location
    {June 2017 – Aug. 2019} % Date(s)
    { 
            \begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Design and Analysis For Complex Industrial Structures \hfill		}
	      \end{cvitems}
	      }
\end{cventries}
\vspace{10pt} 
     
%---------------------------------------------------------
\cventry
{\textbf{Graduate Research Assistant} \hspace{4pt} (\textbf{Advisor:} Prof. Mojtaba Azhari, Prof. Saeid Sarrami)} % Job title
{Isfahan University of Technology\\ \textcolor{gray}{Stability Analysis for Composite Plates \& Shells} } % Organization
{Isfahan, Iran} % Location
{2019 - Dec. 2020 } % Date(s)
        { 
	      \begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Advanced Mathematical Modeling For Free Vibration, Thermal and Mechanical Buckling of Functionally Graded Plates (FGM) Resting on Elastic Foundation Using Spline Finite Strip Method and Third Order Shear Deformation Theory (TSDT) \hfill		}
	      \end{cvitems}
	      }
  \vspace{10pt}




\cventry 
%---------------------------------------------------------
    {\textbf{Lecture} } % Job title
    {Isfahan University of Technology, E-learning Center} % Organization
    {Isfahan, Iran} % Location
    {2019 - 2020} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Beginning C++ Programming	\hfill			Sept. 2019 – Dec. 2020 }
		\item {Python Beginner to Expert	\hfill			Jan. 2020 - Apr 2021}
		\item {Python Data Science Packages \& Data visualization	\hfill			Feb. 2021 - Apr 2021 }
	\end{cvitems}   
     }
     
     \vspace{10pt}